Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-05-15 ms.tex
I added a few sentences on the Subaru analysis to parallel the IRAF reduction I'm doing.

>>>>

\section{Subaru Analysis}

The host star \shStar\ has been characterized by both photometry and spectroscopy.
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara}
We decided to re-visit the high resolution spectrum from \citet{kawahara} by downloading the raw data from the Subaru SMOKA database.
